---
title: "Boundary Data Policy"
description: "What boundary data jpmap includes, where it comes from, and how disputed-territory shapes are handled."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boundary Data Policy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`jpmap` separates convenience from data provenance. The package includes small
boundary files so new users can draw maps immediately, and it also provides
helpers for building larger local boundary files from official public sources.

## Bundled Boundary Data

The installed package includes:

- all-Japan prefecture example boundaries used by default for prefecture maps;
- official MLIT N03 municipal boundaries for Okinawa Prefecture as of
  January 1, 2024;
- disputed-territory shapes that can be excluded with
  `territorial_disputes = FALSE`.

You can see the available bundled and local GeoPackage files with:

```{r}
library(jpmap)

available_jpmap_data()[c("year", "pref_code", "prefecture")]
```

The website intentionally does not print the user-specific data directory.
Run `jpmap_data_dir(create = FALSE)` locally when you need to inspect where
your own generated boundary files are saved.

## Official Municipal Boundaries

Municipality maps are based on Japan's MLIT National Land Numerical
Information N03 administrative area data:

- MLIT N03 2024 page: <https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-N03-2024.html>
- national 2024 archive: <https://nlftp.mlit.go.jp/ksj/gml/data/N03/N03-2024/N03-20240101_GML.zip>
- Okinawa 2024 archive: <https://nlftp.mlit.go.jp/ksj/gml/data/N03/N03-2024/N03-20240101_47_GML.zip>

Build one prefecture when you only need one prefecture:

```{r, eval = FALSE}
jpmap_build_data(year = 2024, prefecture = "Ehime")
```

Build the national file only when you need all municipalities:

```{r, eval = FALSE}
jpmap_build_data(year = 2024)
```

`jpmap_build_data()` converts the source archive to a GeoPackage with two
layers, `prefectures` and `municipalities`.

## Disputed-Territory Shapes

Disputed-territory shapes are politically sensitive because inclusion and
exclusion are both meaningful map choices. Exclude them explicitly when that is
the right display choice:

```{r}
plot_jpmap("prefecture", territorial_disputes = FALSE)
```

You can also include selected areas:

```{r, eval = FALSE}
plot_jpmap("prefecture", territorial_disputes = "senkaku")
plot_jpmap("prefecture", territorial_disputes = c("senkaku", "takeshima"))
```

The disputed-territory layer is a cartographic display layer. It is not a legal
statement about sovereignty. The layer exists so users can make an explicit and
documented display choice rather than relying on inconsistent small-island and
reef handling across data sources.

## Reproducibility

For a reproducible project, record:

- the `jpmap` package version;
- the boundary data year;
- whether boundaries came from bundled files or locally built files;
- whether `territorial_disputes` was `FALSE`, `TRUE`, or a selected character
  vector;
- any simplification tolerance used when building local data.

For example:

```{r, eval = FALSE}
sessionInfo()
available_jpmap_data()[c("year", "pref_code", "prefecture")]
```
