---
title: "Boundary Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boundary Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`jpmap` can work with detailed administrative boundaries, but nationwide
municipal polygons are large. The installed package therefore includes
lightweight example data: Natural Earth prefectures for all of Japan and
Geoshape municipal boundaries for Okinawa.

## Data Directory

Use `jpmap_data_dir()` to find the default local data directory.

```{r}
library(jpmap)
jpmap_data_dir(create = FALSE)
```

## Building Data

Boundary files can be built from Japan's official MLIT National Land Numerical
Information N03 administrative area data. The national 2024 source archive is
about 583 MB, so a full national build is an explicit user-run step.

```{r, eval = FALSE}
jpmap_build_data(year = 2024)
```

When you only need one prefecture, build a smaller prefecture-specific file
from the same official source.

```{r, eval = FALSE}
jpmap_build_data(year = 2024, prefecture = "Ehime")
jpmap_build_data(year = 2024, prefecture = "沖縄県")
```

## jpndistrict

If you already use `jpndistrict`, its `sf` output can be transformed into the
same coordinate system used by `jpmap`. `jpndistrict` is not a hard dependency
because it is not currently available from CRAN, but it is a useful companion
for workflows that already use it.

```{r, eval = FALSE}
library(jpndistrict)

ehime <- jpn_cities(38)
ehime_jpmap <- jpmap_transform(ehime, inset = FALSE)
```

## Available Data

After building or placing a GeoPackage in the data directory, inspect available
years with:

```{r}
available_jpmap_data()
```

The expected file name patterns are `jpmap_boundaries_YYYY.gpkg` for national
data and `jpmap_boundaries_YYYY_PP.gpkg` for one-prefecture data, with layers
named `prefectures` and `municipalities`.
