---
title: "Boundary Data Policy"
description: "Where jpmap boundary data comes from and how disputed-territory shapes are handled."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boundary Data Policy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`jpmap` separates functionality from large boundary files. The package provides
the plotting, joining, transformation, and download helpers. Boundary
GeoPackages can come from the companion `jpmapdata` package or from local files
you build from official public sources.

## Boundary Data Locations

`jpmap` checks:

- GeoPackage files installed by the companion `jpmapdata` package;
- GeoPackage files saved in `jpmap_data_dir()`;
- a custom `data_dir` when you pass one.

You can see the available GeoPackage files with:

```{r}
library(jpmap)

available_jpmap_data()[c("year", "pref_code", "prefecture", "source")]
```

The website intentionally does not print the user-specific data directory.
Run `jpmap_data_dir(create = FALSE)` locally when you need to inspect where
your own generated boundary files are saved.

## Official Municipal Boundaries

Municipality maps are based on Japan's MLIT National Land Numerical
Information N03 administrative area data:

- MLIT N03 2024 page: <https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-N03-2024.html>
- national 2024 archive: <https://nlftp.mlit.go.jp/ksj/gml/data/N03/N03-2024/N03-20240101_GML.zip>
- Okinawa 2024 archive: <https://nlftp.mlit.go.jp/ksj/gml/data/N03/N03-2024/N03-20240101_47_GML.zip>

Build one prefecture when you only need one prefecture:

```{r, eval = FALSE}
jpmap_build_data(year = 2024, prefecture = "Ehime")
```

Build the national file only when you need all municipalities:

```{r, eval = FALSE}
jpmap_build_data(year = 2024)
```

`jpmap_build_data()` converts the source archive to a GeoPackage with two
layers, `prefectures` and `municipalities`.

## Disputed-Territory Shapes

Disputed-territory shapes are politically sensitive because inclusion and
exclusion are both meaningful map choices. Users can exclude them explicitly
when that is the right display choice:

```{r, eval = FALSE}
plot_jpmap("prefecture", territorial_disputes = FALSE)
```

You can also include selected areas:

```{r, eval = FALSE}
plot_jpmap("prefecture", territorial_disputes = "senkaku")
plot_jpmap("prefecture", territorial_disputes = c("senkaku", "takeshima"))
```

The disputed-territory layer is a cartographic display layer. It is not a legal
statement about sovereignty. The layer exists so users can make an explicit and
documented display choice rather than relying on inconsistent small-island and
reef handling across data sources.

## Reproducibility

For a reproducible project, record:

- the `jpmap` package version;
- the boundary data year;
- whether boundaries came from `jpmapdata`, local files, or a custom data
  directory;
- whether `territorial_disputes` was `FALSE`, `TRUE`, or a selected character
  vector;
- any simplification tolerance used when building local data.

For example:

```{r, eval = FALSE}
sessionInfo()
available_jpmap_data()[c("year", "pref_code", "prefecture", "source")]
```
