---
title: "Boundary Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boundary Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`jpmap` stores map boundaries outside the installed package. This keeps the
package small while still allowing detailed prefecture and municipal maps.
The installed package includes lightweight example data: Natural Earth
prefectures for all of Japan and Geoshape municipal boundaries for Okinawa.

## Data Directory

Use `jpmap_data_dir()` to find the default local data directory.

```{r}
library(jpmap)
jpmap_data_dir(create = FALSE)
```

## Building Data

Boundary files can be built from Japan's MLIT National Land Numerical
Information N03 administrative area data.

```{r, eval = FALSE}
jpmap_build_data(year = 2024)
```

The 2024 source archive is about 583 MB, so this command is intentionally a
user-run step.

## Available Data

After building or placing a GeoPackage in the data directory, inspect available
years with:

```{r}
available_jpmap_data()
```

The expected file name pattern is `jpmap_boundaries_YYYY.gpkg`, with layers
named `prefectures` and `municipalities`.
