---
title: "Download Boundary Data"
description: "Understand the bundled Okinawa municipal data and build larger MLIT N03 boundary files locally."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Download Boundary Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
```

`jpmap` uses GeoPackage files with two layers:

- `prefectures`
- `municipalities`

The installed package includes an all-Japan prefecture example layer and an
official Okinawa municipal layer from MLIT N03 administrative area data. The
Okinawa municipal boundaries bundled with the package are the 2024 MLIT N03
Okinawa file, whose administrative boundaries are current as of January 1,
2024.

## Where Files Are Saved

By default, `jpmap_build_data()` saves converted GeoPackage files in the
package data directory returned by `jpmap_data_dir()`.

```{r, eval = FALSE}
library(jpmap)

# Run this locally to see your user-specific data directory.
jpmap_data_dir(create = FALSE)
```

The exact value is different on each computer, so the website does not print a
live path. You do not need to create this directory by hand.
`jpmap_build_data()` creates it when needed.

## Build One Prefecture

For most municipal examples, start with one prefecture. This downloads a
smaller official MLIT N03 archive, converts it to a GeoPackage, and saves it in
`jpmap_data_dir()`.

```{r, eval = FALSE}
jpmap_build_data(year = 2024, prefecture = "Ehime")
```

The generated file is named with the prefecture code:

```r
jpmap_boundaries_2024_38.gpkg
```

For Okinawa, the package already includes the 2024 file:

```r
jpmap_boundaries_2024_47.gpkg
```

## Build All Municipalities

Build nationwide municipal data only when you need all municipalities. The
official 2024 national source archive is about 583 MB, and the converted
GeoPackage is also large.

```{r, eval = FALSE}
jpmap_build_data(year = 2024)
```

The generated national file is named:

```r
jpmap_boundaries_2024.gpkg
```

## Source URLs

The source is MLIT National Land Numerical Information N03 administrative area
data:

- 2024 data page: <https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-N03-2024.html>
- national 2024 archive: <https://nlftp.mlit.go.jp/ksj/gml/data/N03/N03-2024/N03-20240101_GML.zip>
- Okinawa 2024 archive: <https://nlftp.mlit.go.jp/ksj/gml/data/N03/N03-2024/N03-20240101_47_GML.zip>

The filename pattern is `N03-YYYY0101_GML.zip` for national data and
`N03-YYYY0101_PP_GML.zip` for one-prefecture data, where `PP` is a two-digit
prefecture code.

## Custom Location

If you want to keep boundary data in a project folder instead of the default
user data directory, pass `destdir`.

```{r, eval = FALSE}
dir.create("jpmap-data", showWarnings = FALSE)
jpmap_build_data(year = 2024, prefecture = "Ehime", destdir = "jpmap-data")
```

Use the same folder later with `data_dir`.

```{r, eval = FALSE}
jp_map("municipality", include = "Ehime", data_dir = "jpmap-data")
```
