---
title: "Introduction"
description: "Install jpmap and learn the three basic functions: plot a map, load map data, and transform coordinates."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
```

`jpmap` follows the same basic workflow as `usmap`: plot a map, get the map
data, and transform your own coordinates into the same coordinate system.

Install the development version from GitHub:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("yhoriuchi/jpmap")
```

```{r}
library(tidyverse)
library(jpmap)
```

The main plotting function is `plot_jpmap()`. These two calls draw empty maps
without adding data, labels, colors, or other options.

```{r, eval = FALSE}
plot_jpmap("prefecture")
plot_jpmap("municipality", include = "Okinawa")
```

The data function is `jp_map()`, which returns an `sf` object.

```{r, eval = FALSE}
prefectures <- jp_map("prefecture")
okinawa_municipalities <- jp_map("municipality", include = "Okinawa")
```

The transform function is `jpmap_transform()`.

```{r}
places <- tribble(
  ~place, ~lon, ~lat,
  "Tokyo", 139.767, 35.681,
  "Naha", 127.681, 26.212,
  "Ogasawara", 142.191, 27.094
)

places |>
  jpmap_transform(output_names = c("x", "y"))
```

By default, the transform moves Okinawa and Ogasawara into visible inset
locations. Use `inset = FALSE` for a literal projected map, or pass a character
vector such as `inset = "okinawa"` to transport only selected island groups.
You can also use `okinawa = FALSE` or `ogasawara = FALSE`. `plot_jpmap()`
draws inset boxes by default; set `inset_boxes = FALSE` to remove them. Use
`xlim`, `ylim`, `x_breaks`, `y_breaks`, `x_labels`, and `y_labels` when you
want to customize the displayed longitude/latitude frame.
