---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`jpmap` follows the same basic workflow as `usmap`: get a map, plot a map, and
transform user data into the same coordinate system.

```{r}
library(jpmap)
```

The main plotting function is `plot_jpmap()`.

```{r, eval = FALSE}
plot_jpmap("prefectures")
plot_jpmap("municipalities", include = "Okinawa")
```

The data function is `jp_map()`, which returns an `sf` object.

```{r, eval = FALSE}
prefectures <- jp_map("prefectures")
okinawa_municipalities <- jp_map("municipalities", include = "Okinawa")
```

The transform function is `jpmap_transform()`.

```{r}
places <- data.frame(
  place = c("Tokyo", "Naha", "Ogasawara"),
  lon = c(139.767, 127.681, 142.191),
  lat = c(35.681, 26.212, 27.094)
)

jpmap_transform(places, output_names = c("x", "y"))
```

By default, the transform moves Okinawa and Ogasawara into visible inset
locations. Use `inset = FALSE` for a literal projected map, or pass a character
vector such as `inset = "okinawa"` to transport only selected island groups.
You can also use `okinawa = FALSE` or `ogasawara = FALSE`.
