---
title: "Import Boundary Data"
description: "Load companion or locally built boundary GeoPackages with jp_map(), plot_jpmap(), and sf."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import Boundary Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
```

Use `available_jpmap_data()` to see which boundary files `jpmap` can find.

```{r}
library(jpmap)
available <- available_jpmap_data()
jpmap_has_boundary_data <- nrow(available) > 0
jpmap_has_okinawa_data <- any(available$year == 2024 & available$pref_code == "47")
available_summary <- available[c("year", "pref_code", "prefecture", "source")]
row.names(available_summary) <- NULL
available_summary
```

The package checks two locations:

- GeoPackage files installed by the companion `jpmapdata` package;
- files saved in `jpmap_data_dir()`, unless you pass a custom `data_dir`.

## Load Prefecture Data

`jp_map()` returns an `sf` object. Without extra options, prefecture maps use
the first available all-Japan prefecture file.

```{r, eval = jpmap_has_boundary_data}
prefectures <- jp_map("prefecture")
prefectures
```

## Load Okinawa Municipal Data

The companion data package can provide official MLIT N03 municipal boundaries
for Okinawa Prefecture as of January 1, 2024.

```{r, eval = jpmap_has_okinawa_data}
okinawa_municipalities <- jp_map("municipality", include = "Okinawa")
okinawa_municipalities
```

This works without `data_year` or `data_dir` when `jpmap` can see the Okinawa
file through `jpmapdata` or `jpmap_data_dir()`.

## Load Locally Built Municipal Data

After building a local file, use the same `include` value to select the
prefecture.

```{r, eval = FALSE}
jpmap_build_data(year = 2024, prefecture = "Ehime")
ehime_municipalities <- jp_map("municipality", include = "Ehime", data_year = 2024)
```

If you saved the file somewhere else, pass that folder as `data_dir`.

```{r, eval = FALSE}
ehime_municipalities <- jp_map(
  "municipality",
  include = "Ehime",
  data_year = 2024,
  data_dir = "jpmap-data"
)
```

## Inspect A GeoPackage

The GeoPackage layers are ordinary spatial data layers, so you can inspect them
with `sf`.

```{r, eval = jpmap_has_okinawa_data}
okinawa_file <- available$path[available$year == 2024 & available$pref_code == "47"]

sf::st_layers(okinawa_file)
```

Read a layer directly only when you need lower-level control. Most map
workflows can use `jp_map()` instead.

```{r, eval = FALSE}
municipalities <- sf::st_read(okinawa_file, layer = "municipalities")
```

## File Names

`jpmap` recognizes these file names:

- `jpmap_boundaries_YYYY.gpkg` for national data;
- `jpmap_boundaries_YYYY_PP.gpkg` for one-prefecture data.

The `PP` suffix is the two-digit prefecture code, such as `38` for Ehime and
`47` for Okinawa.
