---
title: "Okinawa and Ogasawara Insets"
description: "Include, exclude, or show Okinawa and Ogasawara as transported insets."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Okinawa and Ogasawara Insets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  dpi = 120,
  fig.bg = "white",
  dev.args = list(bg = "white")
)
```

By default, `jpmap` transports Okinawa and Ogasawara into visible inset
locations.

```{r}
library(ggplot2)
library(jpmap)
```

```{r default-insets}
plot_jpmap("prefecture") +
  labs(title = "Default map with Okinawa and Ogasawara insets") +
  theme(
    plot.title = element_text(face = "bold", color = "#2C2A29")
  )
```

## Remove One Inset

Use `ogasawara = FALSE` when you only want Okinawa moved.

```{r okinawa-only}
plot_jpmap(
  "prefecture",
  ogasawara = FALSE
) +
  labs(title = "Okinawa inset only") +
  theme(
    plot.title = element_text(face = "bold", color = "#2C2A29")
  )
```

Use `okinawa = FALSE` when you only want Ogasawara moved.

```{r ogasawara-only}
plot_jpmap(
  "prefecture",
  okinawa = FALSE
) +
  labs(title = "Ogasawara inset only") +
  theme(
    plot.title = element_text(face = "bold", color = "#2C2A29")
  )
```

## Remove The Boxes

Set `inset_boxes = FALSE` to keep the transported islands but remove the
visual frames.

```{r no-boxes}
plot_jpmap(
  "prefecture",
  inset_boxes = FALSE
) +
  labs(title = "Insets without boxes") +
  theme(
    plot.title = element_text(face = "bold", color = "#2C2A29")
  )
```

## Use Literal Geography

Set `inset = FALSE` to keep every geometry in its projected geographic
location.

```{r literal-map}
plot_jpmap(
  "prefecture",
  inset = FALSE
) +
  labs(title = "Projected map without transported insets") +
  theme(
    plot.title = element_text(face = "bold", color = "#2C2A29")
  )
```

## What The Boxes Mean

The inset boxes are visual guide frames for the transported island groups. They
are not legal boundary extents, and they should not be read as a promise that
every island in every source layer is inside a box.

For Okinawa municipal maps, the bundled 2024 MLIT N03 Okinawa layer is
transported as Okinawa. For Ogasawara, the default box is meant to frame the
main Ogasawara inset cluster. Some Tokyo islands in source data, especially
the Izu Islands and very remote islands such as Minamitorishima or
Okinotorishima when present, may appear outside that box or outside the
default plotting frame. Use `inset = FALSE` when complete geographic placement
matters more than a compact display.
