---
title: "Municipal Choropleths"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Municipal Choropleths}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 6,
  dpi = 120,
  fig.bg = "white",
  dev.args = list(bg = "white")
)
```

This article shows the basic workflow for observation-style data: draw
municipal boundaries, count records by municipality, make a choropleth, and add
longitude/latitude points. The example records below are synthetic.

```{r}
library(ggplot2)
library(jpmap)

example_data_dir <- system.file("extdata", package = "jpmap")

okinawa_municipalities <- jp_map(
  "municipalities",
  include = "Okinawa",
  data_year = 2021,
  data_dir = example_data_dir,
  inset = FALSE
)

observations <- data.frame(
  species = c(
    rep("Example species A", 12),
    rep("Example species B", 10),
    rep("Example species C", 8)
  ),
  municipality = c(
    "Naha", "Naha", "Naha", "Urasoe", "Ginowan", "Tomigusuku",
    "Itoman", "Nanjo", "Okinawa", "Uruma", "Nago", "Kunigami",
    "Naha", "Urasoe", "Ginowan", "Ginowan", "Chatan", "Kadena",
    "Yomitan", "Okinawa", "Uruma", "Nago",
    "Itoman", "Nanjo", "Yaese", "Haebaru", "Nishihara", "Onna",
    "Motobu", "Nakijin"
  ),
  lon = c(
    127.681, 127.690, 127.700, 127.715, 127.760, 127.670,
    127.670, 127.770, 127.805, 127.855, 127.985, 128.220,
    127.675, 127.720, 127.755, 127.765, 127.765, 127.750,
    127.745, 127.800, 127.875, 128.010,
    127.675, 127.755, 127.720, 127.730, 127.755, 127.850,
    127.900, 127.930
  ),
  lat = c(
    26.212, 26.220, 26.230, 26.245, 26.275, 26.170,
    26.120, 26.160, 26.335, 26.365, 26.590, 26.745,
    26.215, 26.250, 26.275, 26.285, 26.315, 26.360,
    26.395, 26.335, 26.380, 26.600,
    26.125, 26.165, 26.150, 26.195, 26.225, 26.500,
    26.655, 26.685
  ),
  stringsAsFactors = FALSE
)

observations_xy <- jpmap_transform(
  observations,
  output_names = c("x", "y"),
  inset = FALSE
)

okinawa_view <- jpmap_transform(
  data.frame(
    lon = c(127.55, 128.35, 127.55, 128.35),
    lat = c(26.05, 26.05, 26.85, 26.85)
  ),
  output_names = c("x", "y"),
  inset = FALSE
)
```

## Municipal Boundaries

```{r municipal-boundaries}
ggplot(okinawa_municipalities) +
  geom_sf(fill = "#F7F1E4", color = "white", linewidth = 0.25) +
  geom_sf(fill = NA, color = "#782F40", linewidth = 0.35) +
  coord_sf(
    crs = jpmap_crs(),
    xlim = range(okinawa_view$x),
    ylim = range(okinawa_view$y),
    expand = FALSE,
    datum = NA
  ) +
  labs(
    title = "Okinawa municipal boundaries",
    subtitle = "Bundled example layer from Geoshape"
  ) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29")
  )
```

## Point Map

```{r observation-points}
ggplot(okinawa_municipalities) +
  geom_sf(fill = "#F7F1E4", color = "white", linewidth = 0.25) +
  geom_sf(fill = NA, color = "#782F40", linewidth = 0.35) +
  geom_point(
    data = observations_xy,
    aes(x = x, y = y, color = species),
    size = 2.2,
    alpha = 0.8
  ) +
  scale_color_manual(
    values = c(
      "Example species A" = "#782F40",
      "Example species B" = "#CEB888",
      "Example species C" = "#2C2A29"
    ),
    name = NULL
  ) +
  coord_sf(
    crs = jpmap_crs(),
    xlim = range(okinawa_view$x),
    ylim = range(okinawa_view$y),
    expand = FALSE,
    datum = NA
  ) +
  labs(
    title = "Observation points",
    subtitle = "Longitude and latitude are transformed with jpmap_transform()"
  ) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29"),
    legend.position = "right"
  )
```

## Municipal Counts

```{r municipal-counts}
municipality_counts <- aggregate(
  list(records = observations$species),
  observations["municipality"],
  length
)

counts_map <- jp_map(
  "municipalities",
  include = "Okinawa",
  data_year = 2021,
  data_dir = example_data_dir,
  inset = FALSE
)
counts_map <- jp_map_with_data(counts_map, municipality_counts, values = "records")

ggplot(counts_map) +
  geom_sf(aes(fill = records), color = "white", linewidth = 0.25) +
  coord_sf(
    crs = jpmap_crs(),
    xlim = range(okinawa_view$x),
    ylim = range(okinawa_view$y),
    expand = FALSE,
    datum = NA
  ) +
  scale_fill_gradient(
    low = "#F7F1E4",
    high = "#782F40",
    na.value = "#F7F1E4",
    name = "Records"
  ) +
  labs(
    title = "Municipal choropleth",
    subtitle = "Observation records counted by municipality"
  ) +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29")
  )
```

## Faceted Counts

```{r faceted-counts}
species_counts <- aggregate(
  list(records = observations$species),
  observations[c("species", "municipality")],
  length
)

species_maps <- lapply(unique(observations$species), function(species) {
  counts <- species_counts[species_counts$species == species, ]
  map <- okinawa_municipalities
  map$species <- species
  map$records <- counts$records[match(map$municipality, counts$municipality)]
  map$records[is.na(map$records)] <- 0L
  map
})
species_maps <- do.call(rbind, species_maps)

ggplot(species_maps) +
  geom_sf(aes(fill = records), color = "white", linewidth = 0.2) +
  coord_sf(
    crs = jpmap_crs(),
    xlim = range(okinawa_view$x),
    ylim = range(okinawa_view$y),
    expand = FALSE,
    datum = NA
  ) +
  facet_wrap(~species) +
  scale_fill_gradient(
    low = "#F7F1E4",
    high = "#782F40",
    name = "Records"
  ) +
  labs(
    title = "Municipal choropleths by category",
    subtitle = "The same pattern works for species, years, survey waves, or any grouping variable"
  ) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    strip.text = element_text(face = "bold", color = "#2C2A29"),
    legend.background = element_rect(fill = "white", color = NA),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29")
  )
```

For full nationwide municipal data, build from the official MLIT N03 source:

```{r, eval = FALSE}
jpmap_build_data(year = 2024)
```

For a single-prefecture workflow like many local observation projects, build
only that prefecture:

```{r, eval = FALSE}
jpmap_build_data(year = 2024, prefecture = "Ehime")
```
