---
title: "Plot Municipal Choropleth Maps"
description: "Use bundled Okinawa municipal boundaries and count U.S. base points by municipality."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot Municipal Choropleth Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 6.5,
  dpi = 120,
  fig.bg = "white",
  dev.args = list(bg = "white")
)
```

The package includes official MLIT N03 municipal boundaries for Okinawa
Prefecture as of January 1, 2024. This example counts selected U.S. base point
locations by municipality and maps one fill variable: `base_count`. The figure
focuses on Okinawa Island so the municipal boundaries and base locations are
legible; the bundled boundary file still contains the rest of Okinawa
Prefecture.

```{r}
library(ggplot2)
library(jpmap)

data("jp_us_military_bases")

okinawa_bases <- jp_us_military_bases[
  jp_us_military_bases$prefecture == "Okinawa" &
    jp_us_military_bases$base != "Okinawa U.S. military facilities",
]

okinawa_main_island <- c(
  "那覇市", "宜野湾市", "浦添市", "名護市", "糸満市", "沖縄市",
  "豊見城市", "うるま市", "南城市", "国頭村", "大宜味村", "東村",
  "今帰仁村", "本部町", "恩納村", "宜野座村", "金武町", "読谷村",
  "嘉手納町", "北谷町", "北中城村", "中城村", "西原町", "与那原町",
  "南風原町", "八重瀬町"
)
okinawa_main_island_min_area <- 5e6

okinawa_file <- available_jpmap_data()
okinawa_file <- okinawa_file$path[
  okinawa_file$year == 2024 & okinawa_file$pref_code == "47"
]

okinawa_wgs84 <- sf::st_read(okinawa_file, layer = "municipalities", quiet = TRUE)
okinawa_wgs84 <- okinawa_wgs84[
  okinawa_wgs84$municipality_ja %in% okinawa_main_island,
]
okinawa_wgs84 <- okinawa_wgs84[
  as.numeric(sf::st_area(okinawa_wgs84)) >= okinawa_main_island_min_area,
]

base_points <- sf::st_as_sf(
  okinawa_bases,
  coords = c("lon", "lat"),
  crs = 4326,
  remove = FALSE
)

base_municipalities <- sf::st_join(
  base_points,
  okinawa_wgs84["municipality_code"],
  left = FALSE
)
base_municipalities <- sf::st_drop_geometry(base_municipalities)

base_counts <- aggregate(
  list(base_count = base_municipalities$base),
  base_municipalities["municipality_code"],
  length
)

okinawa_main_map <- jp_map("municipality", include = "Okinawa", inset = FALSE)
okinawa_main_map <- okinawa_main_map[
  okinawa_main_map$municipality_ja %in% okinawa_main_island,
]
okinawa_main_map <- okinawa_main_map[
  as.numeric(sf::st_area(okinawa_main_map)) >= okinawa_main_island_min_area,
]
okinawa_main_map <- jp_map_with_data(
  okinawa_main_map,
  base_counts,
  values = "base_count"
)
okinawa_main_map$base_count[is.na(okinawa_main_map$base_count)] <- 0L
```

```{r municipal-base-counts}
ggplot(okinawa_main_map) +
  geom_sf(
    aes(fill = base_count),
    color = "grey35",
    linewidth = 0.12
  ) +
  coord_sf(
    crs = jpmap_crs(),
    datum = sf::st_crs(4326)
  ) +
  scale_fill_gradient(
    low = "grey92",
    high = "#782F40",
    name = "Base count"
  ) +
  labs(
    title = "Selected U.S. base points by Okinawa Island municipality",
    caption = "Boundary: MLIT N03 administrative area data, January 1, 2024."
  ) +
  theme_gray() +
  theme(
    axis.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.background = element_rect(fill = "white", color = NA),
    plot.title = element_text(face = "bold", color = "#2C2A29"),
    plot.caption = element_text(color = "#2C2A29", hjust = 0, size = 8)
  )
```

For other prefectures, first build the prefecture's municipal boundaries with
`jpmap_build_data(year = 2024, prefecture = "...")`, then use the same join
pattern.
