---
title: "Transform Data"
description: "Move longitude/latitude data into the same projection and inset layout used by jpmap maps."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Transform Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`jpmap_transform()` moves user data into the same projected coordinate system
used by `plot_jpmap()`.

## Data Frames

```{r}
library(jpmap)

places <- data.frame(
  place = c("Tokyo", "Naha", "Ogasawara"),
  lon = c(139.767, 127.681, 142.191),
  lat = c(35.681, 26.212, 27.094)
)

jpmap_transform(places, output_names = c("x", "y"))
```

## Simple Features

If `data` is an `sf` object, `jpmap_transform()` returns an `sf` object.

```{r}
pts <- sf::st_as_sf(
  places,
  coords = c("lon", "lat"),
  crs = 4326,
  remove = FALSE
)

jpmap_transform(pts)
```

Use `inset = FALSE` when you want only the projected Japan CRS and not the
Okinawa/Ogasawara inset movement.

```{r}
jpmap_transform(places, output_names = c("x", "y"), inset = FALSE)
```

You can also move only one island group.

```{r}
jpmap_transform(places, output_names = c("x", "y"), inset = "okinawa")
jpmap_transform(places, output_names = c("x", "y"), inset = "ogasawara")
```

The same switches can be written as boolean arguments when you want the default
`inset = TRUE` behavior except for one island group.

```{r}
jpmap_transform(places, output_names = c("x", "y"), okinawa = FALSE)
jpmap_transform(places, output_names = c("x", "y"), ogasawara = FALSE)
```
