---
title: "U.S. Military Bases and Prefecture GDP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{U.S. Military Bases and Prefecture GDP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 7,
  dpi = 120,
  fig.bg = "white",
  dev.args = list(bg = "white")
)
```

This example combines two sample datasets:

- `jp_prefecture_gdp`, used to fill prefectures by GDP per capita.
- `jp_us_military_bases`, used to draw selected U.S. military installations
  with point size proportional to the public personnel figure.

The bundled prefecture boundaries come from Natural Earth. They are useful for
examples and website figures; use `jpmap_build_data()` when you need detailed
MLIT municipal boundaries.

```{r}
library(ggplot2)
library(jpmap)

data("jp_prefecture_gdp")
data("jp_us_military_bases")

example_data_dir <- system.file("extdata", package = "jpmap")

bases_xy <- jpmap_transform(
  jp_us_military_bases,
  output_names = c("x", "y")
)
```

```{r military-bases-map}
plot_jpmap(
  "prefectures",
  data = jp_prefecture_gdp,
  values = "gdp_per_capita_jpy",
  data_year = 2021,
  data_dir = example_data_dir,
  color = "white",
  linewidth = 0.25
) +
  geom_point(
    data = bases_xy,
    aes(x = x, y = y, size = personnel),
    shape = 21,
    fill = "#CEB888",
    color = "#782F40",
    alpha = 0.85,
    stroke = 0.7
  ) +
  scale_fill_gradient(
    low = "#F7F1E4",
    high = "#782F40",
    name = "GDP per capita\n(JPY)"
  ) +
  scale_size_area(
    max_size = 12,
    name = "Personnel\n(public estimate)"
  ) +
  labs(
    title = "Selected U.S. military installations in Japan",
    subtitle = "Prefecture fill shows 2021 GDP per capita; points show public personnel estimates",
    caption = paste(
      "Boundary: Natural Earth Admin-1. GDP: OECD 2021 values tabulated on Wikipedia.",
      "Personnel figures are public approximate examples, not official headcounts.",
      sep = "\n"
    )
  ) +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA),
    plot.margin = margin(12, 12, 12, 12),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29"),
    plot.caption = element_text(color = "#2C2A29", hjust = 0, size = 8),
    legend.title = element_text(color = "#2C2A29"),
    legend.text = element_text(color = "#2C2A29"),
    legend.position = "right"
  )
```

The personnel figures are intentionally stored with `personnel_scope` because
public numbers differ in what they count: some refer to active-duty military
personnel, while others include family members, civilian employees, or command
personnel. Treat the dataset as a reproducible package example rather than an
official accounting of U.S. forces in Japan.
