---
title: "U.S. Military Bases and Prefecture GDP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{U.S. Military Bases and Prefecture GDP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 7,
  dpi = 120,
  fig.bg = "white",
  dev.args = list(bg = "white")
)
```

This example combines two sample datasets:

- `jp_prefecture_gdp`, used to fill prefectures by GDP per capita.
- `jp_us_military_bases`, used to draw selected U.S. military installations and
  public personnel figures where those figures have a clear source.

Installation-level personnel counts are not published consistently. The map
therefore uses small dark points for installation locations and larger gold
bubbles only for public personnel figures. The Okinawa bubble is a regional
personnel estimate, not a count for a single base.

The bundled prefecture boundaries come from Natural Earth. The package also
ships Okinawa municipal boundaries from Geoshape so the local base example can
run on the website. Use `jpmap_build_data()` when you need nationwide detailed
municipal boundaries from MLIT N03 data.

```{r}
library(ggplot2)
library(jpmap)

data("jp_prefecture_gdp")
data("jp_us_military_bases")

example_data_dir <- system.file("extdata", package = "jpmap")

bases_xy <- jpmap_transform(
  jp_us_military_bases,
  output_names = c("x", "y")
)

personnel_xy <- bases_xy[
  !is.na(bases_xy$personnel) &
    bases_xy$personnel_geography %in% c("regional", "installation"),
]

context_xy <- bases_xy[
  !is.na(bases_xy$personnel) &
    bases_xy$personnel_geography %in% c("command", "installation-community"),
]

okinawa_municipalities <- jp_map(
  "municipalities",
  include = "Okinawa",
  data_year = 2021,
  data_dir = example_data_dir,
  inset = FALSE
)

okinawa_bases <- jp_us_military_bases[
  jp_us_military_bases$prefecture == "Okinawa" &
    jp_us_military_bases$base != "Okinawa U.S. military facilities",
]
okinawa_bases_xy <- jpmap_transform(
  okinawa_bases,
  output_names = c("x", "y"),
  inset = FALSE
)
okinawa_bases_xy$point_type <- ifelse(
  is.na(okinawa_bases_xy$personnel),
  "Location only",
  ifelse(
    okinawa_bases_xy$personnel_is_base_specific,
    "Base-specific figure",
    "Broader public figure"
  )
)
okinawa_bases_xy$label <- okinawa_bases_xy$base
okinawa_bases_xy$label <- sub("Marine Corps Air Station ", "MCAS ", okinawa_bases_xy$label)
okinawa_bases_xy$label <- sub(" / III Marine Expeditionary Force", "", okinawa_bases_xy$label)
okinawa_bases_xy$label <- sub(" Naval Facility", " Naval", okinawa_bases_xy$label)
okinawa_bases_xy$label_dx <- 8500
okinawa_bases_xy$label_dy <- 0
okinawa_bases_xy$label_dx[okinawa_bases_xy$base == "Camp Gonsalves"] <- -32000
okinawa_bases_xy$label_dy[okinawa_bases_xy$base == "Kadena Air Base"] <- -12000
okinawa_bases_xy$label_dy[okinawa_bases_xy$base == "Camp Courtney / III Marine Expeditionary Force"] <- -18000
okinawa_bases_xy$label_dy[okinawa_bases_xy$base == "Camp Foster"] <- -9000
okinawa_bases_xy$label_dy[okinawa_bases_xy$base == "Marine Corps Air Station Futenma"] <- -13000
okinawa_bases_xy$label_dy[okinawa_bases_xy$base == "Naha Port Facility"] <- -9000

okinawa_view <- jpmap_transform(
  data.frame(
    lon = c(127.55, 128.35, 127.55, 128.35),
    lat = c(26.05, 26.05, 26.85, 26.85)
  ),
  output_names = c("x", "y"),
  inset = FALSE
)
```

```{r military-bases-map}
plot_jpmap(
  "prefectures",
  data = jp_prefecture_gdp,
  values = "gdp_per_capita_jpy",
  data_year = 2021,
  data_dir = example_data_dir,
  color = "white",
  linewidth = 0.25
) +
  geom_point(
    data = bases_xy,
    aes(x = x, y = y),
    shape = 21,
    size = 2.3,
    fill = "#2C2A29",
    color = "white",
    alpha = 0.75,
    stroke = 0.35
  ) +
  geom_point(
    data = personnel_xy,
    aes(x = x, y = y, size = personnel),
    shape = 21,
    fill = "#CEB888",
    color = "#782F40",
    alpha = 0.85,
    stroke = 0.7
  ) +
  geom_point(
    data = context_xy,
    aes(x = x, y = y, size = personnel),
    shape = 21,
    fill = NA,
    color = "#782F40",
    alpha = 0.55,
    stroke = 0.9
  ) +
  scale_fill_gradient(
    low = "#F7F1E4",
    high = "#782F40",
    name = "GDP per capita\n(JPY)"
  ) +
  scale_size_area(
    max_size = 12,
    name = "Personnel\n(public figure)"
  ) +
  labs(
    title = "U.S. military presence in Japan",
    subtitle = "Okinawa is transported into the plotting frame and shown with a regional personnel estimate",
    caption = paste(
      "Boundary: Natural Earth Admin-1. GDP: OECD 2021 values tabulated on Wikipedia.",
      "Small dark dots are installation locations; gold bubbles are public personnel figures.",
      "Hollow bubbles are broader command/community figures and are not additive.",
      sep = "\n"
    )
  ) +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA),
    plot.margin = margin(12, 12, 12, 12),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29"),
    plot.caption = element_text(color = "#2C2A29", hjust = 0, size = 8),
    legend.title = element_text(color = "#2C2A29"),
    legend.text = element_text(color = "#2C2A29"),
    legend.position = "right"
  )
```

The personnel figures are intentionally stored with `personnel_scope` and
`personnel_geography` because public numbers differ in what they count. Treat
the dataset as a reproducible package example rather than an official
accounting of U.S. forces in Japan.

The Okinawa municipal layer lets you inspect the installation locations without
compressing them into a single regional symbol. This local map leaves Okinawa
in its geographic position and clips the view to Okinawa Island.

```{r okinawa-municipal-bases}
ggplot(okinawa_municipalities) +
  geom_sf(fill = "#F7F1E4", color = "white", linewidth = 0.25) +
  geom_sf(fill = NA, color = "#782F40", linewidth = 0.35) +
  geom_point(
    data = okinawa_bases_xy,
    aes(x = x, y = y),
    shape = 21,
    size = 2.2,
    fill = "#2C2A29",
    color = "white",
    alpha = 0.8,
    stroke = 0.35
  ) +
  geom_point(
    data = okinawa_bases_xy[!is.na(okinawa_bases_xy$personnel), ],
    aes(x = x, y = y, size = personnel, fill = point_type),
    shape = 21,
    color = "#782F40",
    alpha = 0.85,
    stroke = 0.75
  ) +
  geom_text(
    data = okinawa_bases_xy,
    aes(x = x + label_dx, y = y + label_dy, label = label),
    size = 2.35,
    color = "#2C2A29",
    hjust = 0,
    check_overlap = TRUE
  ) +
  coord_sf(
    crs = jpmap_crs(),
    xlim = range(okinawa_view$x),
    ylim = range(okinawa_view$y),
    expand = FALSE,
    datum = NA
  ) +
  scale_fill_manual(
    values = c("Base-specific figure" = "#CEB888", "Broader public figure" = "white"),
    name = NULL
  ) +
  scale_size_area(
    max_size = 10,
    name = "Personnel\n(public figure)"
  ) +
  labs(
    title = "U.S. military installations on Okinawa Island",
    subtitle = "Municipal boundaries are bundled as package example data",
    caption = paste(
      "Boundary: Geoshape city boundaries, 2023-01-01, CC BY 4.0.",
      "Base points are approximate public coordinates.",
      "Hollow personnel bubbles are broader command or community figures, not base headcounts.",
      sep = "\n"
    )
  ) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    legend.background = element_rect(fill = "white", color = NA),
    plot.margin = margin(12, 12, 12, 12),
    plot.title = element_text(face = "bold", color = "#782F40"),
    plot.subtitle = element_text(color = "#2C2A29"),
    plot.caption = element_text(color = "#2C2A29", hjust = 0, size = 8),
    legend.title = element_text(color = "#2C2A29"),
    legend.text = element_text(color = "#2C2A29"),
    legend.position = "right"
  )
```
